---
title: "Simple recursive calculations of Fibonacci numbers"
author: "Keith McNulty"
date: "08/07/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

In [this article](https://medium.com/cantors-paradise/two-fascinating-properties-of-the-fibonacci-sequence-8cf0f66aca95) I proved that for any $n, m > 2$, the following holds true for Fibonacci numbers $F_n$:

$$
F_{n + m} = F_mF_{n+1} + F_{m-1}F_n
$$

Now we can easily write a recursive function to calculate an arbitrarily large Fibonacci number based on knowing the first few numbers:

```{r}

fibonacci <- function(x) {
  f <- c(1, 1, 2, 3, 5)
  if (x <= 5) {
    f[x]
  } else {
    n <- ceiling(x/2)
    m <- floor(x/2)
    fibonacci(m)*fibonacci(n+1) + fibonacci(m-1)*fibonacci(n)
  }
}

```

Let's test it, doing our best to display very large numbers in R:

```{r, message = FALSE, warning = FALSE}
library(gmp)
fibonacci(30)
as.bigz(fibonacci(1000))
as.bigz(fibonacci(10000))
```

We can also test that the rule of the Fibonacci sequence hold for very large $n$:

```{r}
fibonacci(1000) + fibonacci(1001) == fibonacci(1002)
fibonacci(10000) + fibonacci(10001) == fibonacci(10002)
```

